---
title: "Course4_Project1"  
output: html_document  
---    
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
       
#### Read the data from the downloaded file

```{r readdata}
activitydata<-read.csv('C:\\Code-Git\\Course4\\activity.csv')

```
   *** 
####What is mean total number of steps taken per day?


```{r historgram, echo=TRUE}
stepsperday<-tapply(activitydata$steps,activitydata$date,sum,na.rm=TRUE)
stepsperday<-stepsperday[!is.na(stepsperday)]
hist(stepsperday,main="Steps per day",col="grey",xlab="steps")
```

  
####Mean and Median of the total number of steps taken per day
```{r Q1, echo=TRUE}
mn<-round(mean(stepsperday),digits=2)
md<-median(stepsperday)
```
  
Mean: `r mn  `  
Median: `r md`  
 
 *** 
####What is the average daily activity pattern?

```{r Q2, echo=TRUE}
avgsteps <- tapply(activitydata$steps, activitydata$interval, mean, na.rm=TRUE, simplify=T)
avgsteps <- data.frame(interval=as.integer(names(avgsteps)), value=avgsteps)
plot(avgsteps$interval,avgsteps$value,type="l",xlab="5-minute interval",ylab="Average across all the days")
Inteval_maxvalue<-avgsteps[avgsteps$value==max(avgsteps$value),1]
abline(v=Inteval_maxvalue,col="red",lwd=2)

```

###### Interval with maximum value = `r Inteval_maxvalue` 
 *** 
  
#### Imputing missing values  
```{r Q3, echo=TRUE}
NAsteps<-is.na(activitydata$steps)
imputevalue<-tapply(activitydata$steps,activitydata$interval,mean,na.rm=TRUE)
activitydata_modified<-activitydata
activitydata_modified$steps[NAsteps]<-imputevalue[as.character(activitydata_modified$interval[NAsteps])]
activtydata_impute<-tapply(activitydata_modified$steps,activitydata_modified$date,sum,na.rm=TRUE)
hist(activtydata_impute,main="Steps per day (missing values imputed)",col="grey",xlab="steps")
```


####Mean and Median of the total number of steps (imputed) taken per day
```{r Q3b, echo=TRUE}
mn1<-mean(activtydata_impute)
md1<-median(activtydata_impute)
```

  
Mean: `r mn1  `  
Median: `r md1`   

 *** 

#### Are there differences in activity patterns between weekdays and weekends?

```{r Q3c, echo=TRUE}
activitydata_modified$day<-as.POSIXct(as.character(activitydata_modified$date),format="%Y-%m-%d")
activitydata_modified$day<-weekdays(activitydata_modified$day)
activitydata_modified$IsweekDay<-ifelse(activitydata_modified$day== "Saturday" | activitydata_modified$day== "Sunday", "weekend", "weekday")
activitydata_modified$IsweekDay<-as.factor(activitydata_modified$IsweekDay)
activitydata_modified_avg<- aggregate(steps ~ interval + IsweekDay, data=activitydata_modified, mean)
library(ggplot2)
qplot(interval,steps,data = activitydata_modified_avg, geom=c("line"),xlab = "Interval", ylab = "# of steps") + facet_wrap(~ IsweekDay, ncol = 1)

```

